---
title: "My Shiny App - PGA"
author: "Diana Giraldo"
date: "August 3, 2020"
output:
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("~/Dropbox/Coursera/data_products/")
library(ggplot2)
```

## Peer-graded Assignment
The shiny app I made generates a cloud of random points in a plane 
following 2 Gaussian distributions.

You can choose if you want to move the existing cloud or if you want to generate a new one by cheching the "Dynamic seed" checkbox,
if this box is unchecked:
```{r, echo=TRUE, message=FALSE}
set.seed(123)
```

## Parameters
 - Number of points `n`
 - Mean x `mu_x`
 - Mean y `mu_y`
 - Standard deviation x `sd_x`
 - Standard deviation y `sd_y`

Fixing these parameters:
```{r, echo=TRUE, message=FALSE}
n <- 1000
mu_x <- 1
mu_y <- 0
sd_x <- 0.5
sd_y <- 1.5
```

## Example

A data frame of random points is generated:
```{r, echo=TRUE, message=FALSE}
D <- data.frame(x = rnorm(n, mean = mu_x, sd = sd_x),
                     y = rnorm(n, mean = mu_y, sd = sd_y))
```

The app runs this code: 
```{r, echo=TRUE, eval=FALSE, message=FALSE, warning = FALSE}
plot <- ggplot(D, aes(x,y)) + 
    geom_point(size = 0.25, colour = "grey30") + 
    theme_bw() + xlim(-5,5) + ylim(-5,5)
      plot
```

## Plot
And produces this plot:
```{r, message=FALSE, warning = FALSE}
plot <- ggplot(D, aes(x,y)) + geom_point(size = 0.25, colour = "grey30") + theme_bw() +
          xlim(-5,5) + ylim(-5,5)
      plot
```





